---
title: "Using Portable Paths"
author: "Matthew Strasiotto"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



# A quick intro

This implementation is supposed to provide portability, for people who want 
automating the processing of data that, for ethics reasons, must remain on
a secure network share. 

The typical reliable solution for programmers needing access to this data would
be to include it in their project repository, or by some other means so they 
could use relative path configuration to access their files. 

This solution makes use of two persistent configuration files so that R can 
find and load files: 
A `local.yaml` file, designed to *never be checked into VCS*, allowing a 
one-time set-up to find the root of the data directory.
And a `shared.yaml` for project wide configuration of the contents within that
directory.

Let's load our library before we get started

```{r}
library(portrpaths)
```


# The configration files

Let's have a quick look at what our configuration files might look like
```{r}
config_dir <- system.file("test_data", "t1", package = "portrpaths")

local_config <- file.path(config_dir, "local.yaml")
shared_config <- file.path(config_dir, "shared.yaml")
```

## The shared config

Let's diplay the shared config
```{r}
for (ln in readLines(shared_config)) print(ln)
```

## The local config

What about the local config?

This is the file that designates just where to look for the root of
the data-share. The rest is done by the first file we saw.

*This should never be checked into VCS.*
```{r}
for (ln in readLines(local_config)) print(ln)
```

On looking at that, we notice you may notice that this particular example
designates `d_root: .PROJECT_ROOT`. 

`.PROJECT_ROOT` is a (the only) special case for designating this root, and 
will set the root to be the root of the current RStudio project and/or git 
repo

Usually, you should specify an absolute path like 
 - `/Volumes/RDS-01/PRJ-STEMI/` (OSX)
 
# Using this config

Now it's time to use this configuration.

Let's load it up, and see what it looks like
```{r}
paths <- PortrPath$new(local_config_path = local_config,
                       shared_config_path = shared_config)

print(paths)
```

## Accessing your paths

Accessing your paths is very simple
```{r}
file_list <- paths$get_file_paths()
print(file_list)
```

To use a single designated path-string, just do
```{r}
encounters <- file_list$encs
print(encounters)
```

